Bullet Data Preparation for LIME Diagnostics Paper

### 2020-09-21 code/02-data-preparation.Rmd
fixed typo

```{r}
rtrees_pred = predict(bulletxtrctr::rtrees, type = "prob")[,2]
new_pred = predict(bulletxtrctr::rtrees, bullet_train_filtered %>% select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2]
new_pred_full = predict(bulletxtrctr::rtrees, bullet_train_raw %>% select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2]
```

@@

```{r}
data.frame(rtrees_pred = sort(rtrees_pred), new_pred = sort(new_pred))
```

>>>>

```{r}
rtrees_pred = predict(bulletxtrctr::rtrees, type = "prob")[,2]
new_pred = predict(bulletxtrctr::rtrees, bullet_train_filtered %>% select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2]
new_pred_full = predict(bulletxtrctr::rtrees, bullet_train_raw %>% select(rownames(bulletxtrctr::rtrees$importance)[]), type = "prob")[,2]
```

@@
